Quantifying sablefish movement in the northeast Pacific

### 2022-01-29 ms/manuscript.tex
git subrepo pull (merge) ms
subrepo:
  subdir:   "ms"
  merged:   "14ead22"
upstream:
  origin:   "https://git.overleaf.com/5eb078b74a86f80001efc257"
  branch:   "master"
  commit:   "6c22476"
git-subrepo:
  version:  "0.4.3"
  origin:   "https://github.com/ingydotnet/git-subrepo"
  commit:   "2f68596"

\subsection{Questions}
\begin{enumerate}
    \item How much do sablefish move among geographic regions? 
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:heat-region-average-pooled}
            \item Notes: standard data and priors
        \end{itemize}
    \item How sensitive are sablefish transition rates to alternative reporting rate assumptions?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-reporting} (SI)
            \item Notes: six model fits---33\% increase or 50\% decrease for one region in each fit
        \end{itemize}
    \item How sensitive are sablefish transition rates to harvest rate priors?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-harvest-priors} (SI)
            \item Notes: five model fits; harvest rate prior sd scaled to mean by progressively wider multiplier
        \end{itemize}    
    \item How much do sablefish transition rates vary by length class?
        \begin{itemize}
            \item Model: \texttt{region-average-length}
            \item Visual: \autoref{fig:heat-region-average-length} (SI)
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates by length class vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season (SI)
            \item Notes: standard data and priors
        \end{itemize}
    \item How much do sablefish transition rates by length class vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year (SI) 
            \item Notes: standard data and priors
        \end{itemize} 
    \item How many sablefish moved between regions each year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO barplot; one panel per border; directional (bars) and net (line) movement
            \item Notes: standard data and priors; abundance at length data (scaled proportional to survey biomass index for Alaska regions)
        \end{itemize}    
    \item What is the relationship between sablefish density and transition rates?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TBD
            \item Notes: TBD ideally use annual biomass estimates as proxy for relative density
        \end{itemize}    
    \item Does the movement model recover known parameters on simulated data adequately?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TBD
            \item Notes: TBD
        \end{itemize}
\end{enumerate}

@@

>>>>

\subsection{Questions}
\begin{enumerate}
    \item How much do sablefish move among geographic regions? 
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:heat-region-average-pooled}
            \item Notes: standard data and priors
        \end{itemize}
    \item How sensitive are sablefish transition rates to alternative reporting rate assumptions?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-reporting} (SI)
            \item Notes: six model fits---33\% increase or 50\% decrease for one region in each fit
        \end{itemize}
    \item How sensitive are sablefish transition rates to harvest rate priors?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-harvest-priors} (SI)
            \item Notes: five model fits; harvest rate prior sd scaled to mean by progressively wider multiplier
        \end{itemize}    
    \item How much do sablefish transition rates vary by length class?
        \begin{itemize}
            \item Model: \texttt{region-average-length}
            \item Visual: \autoref{fig:heat-region-average-length} (SI)
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-pooled}
            \item Visual: \autoref{fig:bar-retention-region-season-pooled} and \autoref{fig:bar-region-season-pooled} 
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: \autoref{fig:point-retention-region-year-pooled} and \autoref{fig:point-region-year-pooled} 
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates by length class vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-length}
            \item Visual: TODO
            \item Notes: standard data and priors
        \end{itemize}
    \item How much do sablefish transition rates by length class vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: \autoref{fig:point-retention-region-year-length} 
            \item Notes: standard data and priors
        \end{itemize} 
    \item How many sablefish moved between regions each year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO barplot; one panel per border; directional (bars) and net (line) movement
            \item Notes: standard data and priors; abundance at length data (scaled proportional to survey biomass index for Alaska regions)
        \end{itemize}    
    \item What is the relationship between sablefish density and transition rates?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TBD
            \item Notes: TBD ideally use annual biomass estimates as proxy for relative density
        \end{itemize}    
    \item Does the movement model recover known parameters on simulated data adequately?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TBD
            \item Notes: TBD
        \end{itemize}
\end{enumerate}

@@

% bar-retention-region-season-pooled
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.7\textwidth]{bar-retention-region-season-pooled.png}
    \caption{}
    \label{fig:bar-retention-region-season-pooled}
\end{figure}

% bar-region-season-pooled
\begin{figure}[htb]
    \centering
    \includegraphics[width = \textwidth]{bar-region-season-pooled.png}
    \caption{}
    \label{fig:bar-region-season-pooled}
\end{figure}

% point-retention-region-year-pooled
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.7\textwidth]{point-retention-region-year-pooled.png}
    \caption{}
    \label{fig:point-retention-region-year-pooled}
\end{figure}

% point-region-year-pooled
\begin{figure}[htb]
    \centering
    \includegraphics[width = \textwidth]{point-region-year-pooled.png}
    \caption{}
    \label{fig:point-region-year-pooled}
\end{figure}

% point-retention-region-year-length
\begin{figure}[htb]
    \centering
    \includegraphics[width = \textwidth]{point-retention-region-year-length.png}
    \caption{}
    \label{fig:point-retention-region-year-length}
\end{figure}
